Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Validation

### 2012-12-05 paper.tex
tweak

We use the Castro code as described in \citet{castro}.  For all the runs,
the PPM reconstruction is done, using the original limiters \citep{ppm}.
The original implementation of the PPM prediction in Castro takes the
form:
\begin{equation}
q_{i+1/2,L}^{n+1/2} = q_i -
   \sum_{\nu;\lambda^{(\nu)}\ge 0} l^{(\nu)} \cdot \left [
        q_i - \mathcal{I}_+(\sigma_\nu)
       \right ] r^{(\nu)}
\end{equation}
where $q$ is the vector of primitive variables, with $q_i$
representing the average in the cell, $l$ and $r$ are the left and
right eigenvectors with eigenvalue $\lambda$.  The sum is over all the
waves that result from the characteristic structure of the problem,
but designed such that only waves moving toward the interface
contribute to the interface value, $q_{i+1/2,L}^{n+1/2}$.  Finally,
$\mathcal{I}_+(\sigma_\nu)$ is the jump carried to the right interface
of the cell by the wave $\nu$, constructed by averaging under the
parabolic interpolant in the cell all information that can reach the
interface over the timestep.  $\sigma$ here is the fraction of the
zone crossed by the wave denoted by $\nu$.  The reader is referred to
\citet{ppmunsplit} for further defaults.

>>>>

We use the Castro code as described in \citet{castro}.  For all the runs,
the PPM reconstruction is done, using the original limiters \citep{ppm}.
The original implementation of the PPM prediction in Castro takes the
form:
\begin{equation}
q_{i+1/2,L}^{n+1/2} = q_i -
   \sum_{\nu;\lambda^{(\nu)}\ge 0} l^{(\nu)} \cdot \left [
        q_i - \mathcal{I}_+(\sigma_\nu)
       \right ] r^{(\nu)}
\end{equation}
where $q$ is the vector of primitive variables, with $q_i$
representing the average in the cell, $l$ and $r$ are the left and
right eigenvectors with eigenvalue $\lambda$.  The sum is over all the
waves that result from the characteristic structure of the problem,
but designed such that only waves moving toward the interface
contribute to the interface value, $q_{i+1/2,L}^{n+1/2}$.  Finally,
$\mathcal{I}_+(\sigma_\nu)$ is the jump carried to the right interface
of the cell by the wave $\nu$, constructed by averaging under the
parabolic interpolant in the cell all information that can reach the
interface over the timestep, with $\sigma$ representing the fraction
of the zone crossed by the wave denoted by $\nu$ during the timestep.
The reader is referred to \citet{ppmunsplit} for further defaults.
